Why does preregistration increase the persuasiveness of evidence? A Bayesian rationalization

### 2023-05-16 manuscript.Rmd
Update manuscript.Rmd
remove places

---
title: "Why does preregistration increase the persuasiveness of evidence? A Bayesian rationalization"
bibliography: references.bib
abstract: "`r paste0(c('\\\\noindent', readLines('abstract.md')), collapse = ' ')`"
shorttitle: "The Objective of Preregistration"
author: 
  - name: Aaron Peikert
    affiliation: "1,2,3"
    email: peikert@mpib-berlin.mpg.de
    corresponding : yes    # Define only one corresponding author
    address: "Center for Lifespan Psychology, Max Planck Institute for Human Development, Lentzeallee 94, 14195 Berlin, Germany"
  - name: Andreas M. Brandmaier
    affiliation: "1, 2, 4"
affiliation:
  - id: 1
    institution: Max Planck Institute for Human Development
  - id: 2
    institution: Max Planck UCL Centre for Computational Psychiatry and Ageing Research
  - id: 3
    institution: Humboldt-Universität zu Berlin
  - id: 4
    institution: MSB Medical School Berlin
keywords: |
  preregistration; confirmation; exploration; hypothesis testing; Bayesian; Open Science
wordcount         : "`r tryCatch(wordcountaddin::word_count(), error = function(x)'~7000')`"
figsintext: false
figurelist: false
tablelist : false
footnotelist: false
lineno: true
linkcolor: "blue"
csquotes: false
class: "man"
documentclass: "apa7"
csl: "`r system.file('rmd', 'apa7.csl', package = 'papaja')`"
output:
  papaja::apa6_pdf:
    latex_engine: xelatex
header-includes: |
  \raggedbottom
  \makeatletter

@@

<!--the current goal of preregistration is confirmation-->
One goal of preregistration that has received widespread attention is to clearly distinguish confirmatory from exploratory research [@mellorEasyPreregistrationWill2018; @nosekPreregistrationRevolution2018; @wagenmakersAgendaPurelyConfirmatory2012; @simmonsPreregistrationWhyHow2021; @bakkerEnsuringQualitySpecificity2020].
In such a narrative, preregistration is justified by a confirmatory research agenda.
However, two problems become apparent under closer inspection.
First, many researchers do not subscribe to a purely confirmatory research agenda.
Second, there is no strict mapping of the categories preregistered vs. non-preregistered onto the categories confirmatory vs. exploratory research.

>>>>

---
title: "Why does preregistration increase the persuasiveness of evidence? A Bayesian rationalization"
bibliography: references.bib
abstract: "`r paste0(c('\\\\noindent', readLines('abstract.md')), collapse = ' ')`"
shorttitle: "The Objective of Preregistration"
author: 
  - name: Aaron Peikert
    affiliation: "1,2,3"
    email: peikert@mpib-berlin.mpg.de
    corresponding : yes    # Define only one corresponding author
    address: "Center for Lifespan Psychology, Max Planck Institute for Human Development, Lentzeallee 94, 14195 Berlin, Germany"
    role:
      - Conceptualization
      - Writing---Original Draft Preparation
      - Writing---Review & Editing
      - Methodology
      - Formal analysis
      - Software
      - Visualization
      - Project administration
  - name: Maximilian S. Ernst
    affiliation: "3"
    role:
      - Writing---Review & Editing
      - Formal analysis
      - Validation
  - name: Andreas M. Brandmaier
    affiliation: "1, 2, 4"
    role:
      - Writing---Review & Editing
      - Supervisions
affiliation:
  - id: 1
    institution: Center for Lifespan Psychology, Max Planck Institute for Human Development
  - id: 2
    institution: Max Planck UCL Centre for Computational Psychiatry and Ageing Research
  - id: 3
    institution: Department of Psychology, Humboldt-Universität zu Berlin
  - id: 4
    institution: Department of Psychology, MSB Medical School Berlin
keywords: |
  preregistration; confirmation; exploration; hypothesis testing; Bayesian; Open Science
wordcount         : "`r tryCatch(wordcountaddin::word_count(), error = function(x)'~7000')`"
figsintext: false
figurelist: false
tablelist : false
footnotelist: false
lineno: true
linkcolor: "blue"
csquotes: false
class: "man"
documentclass: "apa7"
csl: "`r system.file('rmd', 'apa7.csl', package = 'papaja')`"
output:
  papaja::apa6_pdf:
    latex_engine: xelatex
header-includes: |
  \raggedbottom
  \makeatletter

@@

<!--the current goal of preregistration is confirmation-->
One goal of preregistration that has received widespread attention is to clearly distinguish confirmatory from exploratory research [@mellorEasyPreregistrationWill2018; @nosekPreregistrationRevolution2018; @wagenmakersAgendaPurelyConfirmatory2012; @simmonsPreregistrationWhyHow2021; @bakkerEnsuringQualitySpecificity2020].
In such a narrative, preregistration is justified by a confirmatory research agenda.
However, two problems become apparent under closer inspection.
First, many researchers do not subscribe to a purely confirmatory research agenda.
Second, there is strict mapping of the categories preregistered vs. non-preregistered onto the categories confirmatory vs. exploratory research.
